Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-11 02_Paper/paper.tex
5.1 and 5.2

Industrial projects require to work with a variety of sensors and controllers. Thus, there is a risk of incompatibility between technologies. To avoid that problem, universal protocols are often implemented at industrial projects. This is the case for our industry 4.0 demonstration cell, which shares data via the protocol OPC-UA.

Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell. For our case, the data is acquired independently from two OPC-UA servers. This represents the interaction between multiple servers in real production environments.

In our implementation, we acquired the data in two steps.
The first step consisted of listing all the variables of interest and mapping their source. The second step was to determine the use cases of interest. Our study focussed on the data described in Table.~\ref{tab:data_source} and the six use cases described in Table.~\ref{tab:use_cases}. The data was manually collected by using the software "UAExpert - v1.5.1". Approximately 15 hours of data were collected, while equally sampling each use case during the data acquisition time.

@@

Once enough data is collected, the next step is to clean the raw data and organize it accordingly \cite{goodfellow2016deep}. For our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp. Since our systems are not completely synchronized, it was needed to calculate the delta-time between servers by referencing each server's base clock. Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.

Data tags interpretation is an important step in the preprocessing process \cite{goodfellow2016deep}. The raw data collected from the sensors is usually tagged by an alphanumeric code predefined by the sensor manufacture. To work with the data, it was needed to implement diverse functions which have the task to clean the raw data in a more human-readable form. This means to remove samples out of clear boundaries and missing values, as well as to translate the sensor code tags based on a dictionary predefined by the authors. This last step, might be optional in other implementations, however, it proves to be a great addition for testing purposes.

Once the data is clean and compiled in one directory, our step was to split the data based on the assembly cycle. For our purpose, we split the dataset into individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so. At this point, we have a series of data-samples based on time series. However, we are not interested in a time series analysis, since having the time parameter would not neccesarily improve the prediction results, but rather make the approach more complex and more data would be needed, therefore it was needed to compress each time-series based data-sample in an atemporal data-sample.
To eliminate time as a variable in our dataset, we defined a series of rules to be applied in each assembly cycle data-sample:

@@

Each time-series sample was evaluated based on the rules stated above, and the result of each evaluation was considered as our atemporal data-sample, which we used as the base for our classifier.

@@

Based on the MLP prediction results presented on Table.~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%. The false-negative results represent the 12\% of the test sample and the true predictions constitute 88\% of the test data.

The outcome of the models shows that the random forest performed best followed by the multilinear perceptron and the support vector machine. However, by reviewing the confusion matrices presented in Table.~\ref{tab:Confusion_matrix}, multilinear perceptron would be the preferred solution to be implemented at industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.

>>>>

Industrial projects require to work with a variety of sensors and controllers from different manufacturers. Thus, there is a risk of incompatibility between technologies. To avoid that problem, universal protocols are often implemented in industrial projects. This is the case for our industry 4.0 demonstration cell, which shares data via the protocol OPC-UA.

The Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell. In our case, the data is acquired independently from two OPC-UA servers. This represents the interaction between multiple servers in real production environments.

Before collecting the data, we need to find the variables of interest and mapping their source, as well as to determine the use cases of interest. Our study focussed on the data described in Table~\ref{tab:data_source} and the six use cases described in Table~\ref{tab:use_cases}. The data was manually collected by using the software "UAExpert - v1.5.1". Approximately 15 hours of data were collected in different sessions, while equally sampling each use case during the data acquisition stage.

@@

Once the data was collected, the next step was to clean the raw data and organize it accordingly \cite{goodfellow2016deep}. In our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp. Since our systems were not completely synchronized, as common in practice, it was needed to calculate the delta-time between servers by referencing each server's base clock. Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.

Data tags interpretation is an important step in the preprocessing process \cite{goodfellow2016deep}. The raw data collected from the sensors is usually tagged by an alphanumeric code predefined by the sensor manufacturer. To work with the data, it was needed to implement diverse functions which have the task to clean the raw data in a more human-readable form. This means to remove samples out of clear boundaries and missing values, as well as to translate the sensor code tags based on human-readable words predefined by the authors. This last step, might be optional in other implementations, however, it proves to be a great addition for testing purposes.

Once the data is clean and compiled in one directory, the next step was to split the data based on the assembly cycle. For our purpose, we split the dataset into individual data-samples with help of the action tags included in the dataset Table~\ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so. At this point, we have a series of data-samples based on time series. However, we are not interested in a time series analysis, since having the time parameter would not necessarily improve the prediction results, but rather make the approach more complex, and more data would be needed, therefore it was needed to compress each time-series based data-sample into atemporal data-samples.

Each time-series sample collected is the result of data collected during one machine assembly cycle (MAC). The starting point of one MAC is the very first moment the robotic arm grabs the black disk from the store area and the ending point is before grabbing the next black disk in the same area.
To eliminate time as a variable in our dataset, it was needed to acquire the data at specific moments of the MAC. For that reason, we defined a set of sampling-conditions that helped us to collect the relevant data during the MAC:

@@

Each time-series sample was evaluated based this sampling-condition, and the result of each evaluation was considered as our atemporal data-sample, which we used as the base for our classifier.

@@

Based on the MLP prediction results presented on Table~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%. The false-negative results represent the 12\% of the test sample and the true predictions constitute 88\% of the test data.

The outcome of the models shows that the random forest performed best followed by the multilinear perceptron and the support vector machine. However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, multilinear perceptron would be the preferred solution to be implemented at industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
